---
title: "Introduction to tsCeatures"
author: "Trent Henderson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to tsCeatures}
  %\VignetteEngine{knitr::knitr}
  %\usepackage[UTF-8]{inputenc}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.height = 7,
  fig.width = 9
)
```

`tsCeatures` is a simple R package for the computation of a few time-series features coded in C++ for scalability and efficiency. The name is a play on the `tsfeatures` naming convention in the time series software world. You can install `tsCeatures` from GitHub:

```{r, message = FALSE, warning = FALSE, eval = FALSE}
devtools::install_github("hendersontrent/tsCeatures")
```

## Core functionality

The main function of the package is `get_features` which automatically computes all features included in `tsCeatures`. This can be run in a one-liner:

```{r, message = FALSE, warning = FALSE}
library(tsCeatures)
x <- rnorm(100)
outs <- get_features(x)
```

You can also calculate each of the features individually by directly calling their name:

```{r, message = FALSE, warning = FALSE}
ac_1(x)
```

A list of the features included in the package and some descriptions of what they are is available as a tidy dataframe called `feature_descriptions`. Here is the first 6 rows:

```{r, message = FALSE, warning = FALSE}
head(feature_descriptions)
```
